Distortion-corrected kernel density estimate on Riemannian manifolds

### 2022-10-04 paper/paper.Rmd
Remove colors for rank comparison

```{r tpisomapvs4ml, fig.align = 'center', out.width = "95%", fig.cap="Comparison of outliers found by ISOMAP and other four manifold learning methods for DC-KDE (on the left panel) and KDE (on the right panel). The four colors and shapes represents the four gaussian kernels in the 2-D meta data. Outliers found by DC-KDE are more consistent regardless of the manifold learning embedding.", echo = FALSE}
knitr::include_graphics("figures/Twin Peak2000_density_comparison_isomapvs4ml_r0_5_rank.png")
```

>>>>

```{r tpisomapvs4ml, fig.align = 'center', out.width = "95%", fig.cap="Comparison of outliers found by ISOMAP and other four manifold learning methods for DC-KDE (on the left panel) and KDE (on the right panel). The four colors and shapes represents the four gaussian kernels in the 2-D meta data. Outliers found by DC-KDE are more consistent regardless of the manifold learning embedding.", echo = FALSE}
knitr::include_graphics("figures/Twin Peak2000_density_compare_isomapvs4ml_radius8_r0_5_rank.png")
```
